{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-14 brains-protocol.tex
rewriting expressions in 4.2, puzzling dependency on f in H_0 / clearer

We introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival_0$ had been chosen randomly from the pool of free association words.
Since $\phi(\warrival_0)$ is in fact a constant in the above averaging (by definition $\warrival_0$ does not depend on $\wstart$) and $\phi(\wstart)=f$, 
the baseline variation under $\mathcal{H}_0$ may be rewritten:
$$\Delta_{\phi}^0 (f) = \left<\phi\right>-f$$

>>>>

We introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival$ has been chosen randomly from the pool of free association words.
In this case, since $\phi(\warrival)$ becomes a constant value in the above averaging (by definition $\warrival$ does not depend on $\wstart$ anymore) and $\phi(\wstart)=f$,  the baseline variation under $\mathcal{H}_0$ may be rewritten as:
$$\Delta_{\phi}^0 (f) = \left<\phi\right>-f$$
